```{r}
#install.packages("shinyjs")
library(shinydashboard)
library(shiny)
library(shinyjs)
library(tidyverse)
library(ggplot2)
library(DT)
library(DBI)
library(shiny)
library(baseballr)
library(dplyr)
```


```{r}

# Function to fetch all data for a given year with detailed error handling
fetch_year_data <- function(year) {
  cat("Fetching data for year:", year, "\n")
  
  # Fetch teams data with error handling
  teams_data <- tryCatch({
    mlb_teams() |>
      mutate(year = year)
  }, error = function(e) {
    cat(sprintf("Error fetching teams data: %s\n", e$message))
    return(data.frame())
  })
  
  # Helper function to safely fetch and process stats with detailed error logging
  fetch_stats <- function(stat_group) {
    tryCatch({
      cat(sprintf("Attempting to fetch %s stats for year %d...\n", stat_group, year))
      
      # Print the arguments being used
      cat(sprintf("Parameters: season=%d, stat_type=season, stat_group=%s\n", 
                  year, stat_group))
      
      result <- try(mlb_teams_stats(stat_type = 'season', stat_group = as.character(stat_group),
                                    season = as.numeric(year)))
        
      
      if (is.null(result) || nrow(result) == 0) {
        cat(sprintf("Warning: No data returned for %s stats in %d\n", stat_group, year))
        return(data.frame())
      }
      
      return(result |> mutate(year = year))
      
    }, error = function(e) {
      cat(sprintf("Error fetching %s stats for year %d: %s\n", 
                  stat_group, year, e$message))
      
      # Try to print more information about the error
      cat("Error details:\n")
      print(e)
      
      return(data.frame())
    })
  }
  
  # Fetch stats with delay between calls to avoid rate limiting
  cat("\nFetching hitting stats...\n")
  hitting_stats <- fetch_stats("hitting")
  Sys.sleep(2)  # Add delay between calls
  
  cat("\nFetching pitching stats...\n")
  pitching_stats <- fetch_stats("pitching")
  Sys.sleep(2)  # Add delay between calls
  
  cat("\nFetching fielding stats...\n")
  fielding_stats <- fetch_stats("fielding")
  
  # Check if we got any data
  cat("\nData fetch summary:\n")
  # cat("Teams data rows:", nrow(teams_data), "\n")
  cat("Hitting stats rows:", nrow(hitting_stats), "\n")
  cat("Pitching stats rows:", nrow(pitching_stats), "\n")
  cat("Fielding stats rows:", nrow(fielding_stats), "\n")
  
  # Return as list
  list(
    teams = teams_data,
    hitting = hitting_stats,
    pitching = pitching_stats,
    fielding = fielding_stats
  )
}

```

```{r}


test_fetch <- fetch_year_data(2023)

```
```{r}

# Function to save or update consolidated data
save_consolidated_data <- function(years_to_fetch) {
  # File paths
  #teams_file <- "../data-raw/teams_data.rds"
  hitting_file <- "../data-raw/hitting_stats.rds"
  pitching_file <- "../data-raw/pitching_stats.rds"
  fielding_file <- "../data-raw/fielding_stats.rds"
  
  # Load existing data if it exists
  #existing_teams <- if (file.exists(teams_file)) readRDS(teams_file) else NULL
  existing_hitting <- if (file.exists(hitting_file)) readRDS(hitting_file) else NULL
  existing_pitching <- if (file.exists(pitching_file)) readRDS(pitching_file) else NULL
  existing_fielding <- if (file.exists(fielding_file)) readRDS(fielding_file) else NULL
  
  # Fetch new data for all specified years
  new_data <- map(years_to_fetch, fetch_year_data)
  
  # Combine data from all years
  # combined_teams <- bind_rows(
  #   existing_teams,
  #   map_dfr(new_data, "teams")
  # ) |> distinct()  # Remove any duplicates
  
  combined_hitting <- bind_rows(
    existing_hitting,
    map_dfr(new_data, "hitting")
  ) |> distinct()
  
  combined_pitching <- bind_rows(
    existing_pitching,
    map_dfr(new_data, "pitching")
  ) |> distinct()
  
  combined_fielding <- bind_rows(
    existing_fielding,
    map_dfr(new_data, "fielding")
  ) |> distinct()
  
  # Save consolidated files
  # saveRDS(combined_teams, teams_file)
  saveRDS(combined_hitting, hitting_file)
  saveRDS(combined_pitching, pitching_file)
  saveRDS(combined_fielding, fielding_file)
  
  # Print summary
  cat("\nData consolidation complete!\n")
  # cat("Teams data:", nrow(combined_teams), "rows\n")
  cat("Hitting stats:", nrow(combined_hitting), "rows\n")
  cat("Pitching stats:", nrow(combined_pitching), "rows\n")
  cat("Fielding stats:", nrow(combined_fielding), "rows\n")
}

```



```{r}

# Helper function to load and process team stats
#not sure if we should ever use this function
process_fielding_stats <- function(year, stat_group) {
  # Load the relevant data files
  fielding_df <- readRDS("../data/fielding_data.rds") |> filter(year == !!year)
  
  stats_file <- paste0("../data/", stat_group, "_stats.rds")
  stats_data <- readRDS(stats_file) |> filter(year == !!year)
  
  # Process and combine the data
  if (nrow(stats_data) == 0) return(NULL)
  
  stats_data |>
    left_join(teams_data, by = c("team_id", "year")) |>
    select(team_name, everything(), -team_id) |>
    arrange(team_name)
}




```


```{r}
years_to_fetch <- 1973:2023
save_consolidated_data(years_to_fetch)

```
```{r}
hitting_df <- readRDS("../data-raw/hitting_stats.rds")
#teams_df <- readRDS("../data-raw/teams_data.rds")
fielding_df <- readRDS("../data-raw/fielding_stats.rds")
pitching_df <- readRDS("../data-raw/pitching_stats.rds")
```

```{r}
glimpse(hitting_df)
glimpse(teams_df)
glimpse(fielding_df)
glimpse(pitching_df)

```
```{r}
unique(teams_df$sport_name)
nrow(teams_df)
teams_df |> filter(sport_name == "Major League Baseball") -> mlb_team_df


#mlb_team_df needs to just be a data table at the bottom where you can look up stats about the teams
mlb_team_df |> select(-c(all_star_status, link, season, file_code, short_name, franchise_name, club_name, active, venue_link, league_id, league_link, division_link, sport_link, spring_league_link, spring_venue_link)) -> team_facts_df



pitching_df |> select(c(year, team_id, win_percentage, rank, games_played, games_started, games_finished, wins, losses)) -> win_stats_df

glimpse(mlb_team_df)

```
#one table of team facts 

# one visualization for team hitting, one for team pitching, one for team fielding, sidebar to filter page by team and by year, option to select metrics for visualization for each

#one visualization with team performance based on selected metrics, bar graph by team for single numerical variables, line, copy the other metrics from other project for categorical variable visualization, combine hitting and pitching stats, 

similar visualization for hitting stats


simliar visualization for pitching_stats


```{r}
#remove non MLB teams from dataset
glimpse(hitting_df)
glimpse(pitching_df)
glimpse(fielding_df)

pitching_df |> select(-c(team_link, splits_tied_with_offset, splits_tied_with_limit, type_display_name, season)) -> pitching_df
hitting_df |> select(-c(team_link, splits_tied_with_offset, splits_tied_with_limit, type_display_name, season)) -> hitting_df
fielding_df |> select(-c(team_link, splits_tied_with_offset, splits_tied_with_limit, type_display_name, season)) -> fielding_df

mlb_team_df
pitching_df |> filter(team_id %in% mlb_team_df$team_id)  |> select(-c(team_link, splits_tied_with_offset, splits_tied_with_limit))-> pitching_df
# hitting_df |> filter(team_id %in% mlb_team_df$team_id) |> select(-c(team_link, splits_tied_with_limit, splits_tied_with_offset)) -> hitting_df
# 
# fielding_df |> filter(team_id %in% mlb_team_df$team_id) |> select(-c(team_link, splits_tied_with_limit, splits_tied_with_offset)) -> fielding_df
```

```{r}
mlb_team_df |> select(-c(all_star_status, link, season, parent_org_id, venue_id, venue_link, league_id, league_name, league_link, division_id, division_link, sport_id, sport_link, sport_name, spring_league_id, spring_league_link, spring_league_abbreviation, spring_venue_id, spring_venue_link, team_id, team_code, file_code)) -> mlb_team_df

mlb_team_df |> select(-c(parent_org_name, team_code, file_code)) -> mlb_team_df
mlb_team_df |> select(-c(active)) -> mlb_team_df
glimpse(mlb_team_df)
```

```{r}
#save files as RDS to data instead of data_raw
saveRDS(mlb_team_df, "../data/team_stats.rds")
saveRDS(pitching_df, "../data/pitching_stats.rds")
saveRDS(hitting_df, "../data/hitting_stats.rds")
saveRDS(fielding_df, "../data/fielding_stats.rds")



```

```{r}
str(mlb_team_df)
```
```{r}
hitting_df <- readRDS("../data/hitting_stats.rds")

mlb_team_df <- readRDS("../data/team_stats.rds")
pitching_df <- readRDS("../data/pitching_stats.rds")
fielding_df <- readRDS("../data/fielding_stats.rds")
```
```{r}
hitting_df

pitching_df

fielding_df
mlb_team_df
unique(hitting_df$team_id)
unique(pitching_df$team_name)
unique(fielding_df$team_name)


sort(unique(pitching_df$team_id))

mlb_team_codes <- unique(mlb_team_df$team_id)
pitching_df |> filter(team_id %in% mlb_team_codes)


pitching_df |> filter(team_id %in% mlb_team_df$team_id)
```

